Simple Macroeconomic Forecast Distributions

### 2024-10-29 miscellaneous/presentation/presentation.tex
presentation updates

\section{Results}
\begin{frame}{Scores on holdout data 2013-2023 - Inflation}
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/ho_wis_pcpi_pch_absolute_rollingwindow.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

\begin{frame}{Scores on holdout data 2013-2023 - GDP Growth}
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/ho_wis_ngdp_rpch_absolute_rollingwindow.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

\begin{frame}{Calibration - on holdout data 2013-2023}
%\textit{Here, I'll instead map the colors to the different forecast sources (currently mapped to the window method), so we'll just have one plot each}
    %Coverage at the 50\% and 80\% central interval: \\ 
\begin{figure}
  \begin{subfigure}{0.385\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/ho_coverage_pcpi_pch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
  \end{subfigure}
  \hspace*{12mm}
  %\hfill  % maximize separation between the subfigures
  \begin{subfigure}{0.385\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/ho_coverage_ngdp_rpch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
  \end{subfigure}%
\end{figure}

@@

\begin{frame}{Increasing Uncertainty}
%Width of Prediction Intervals, by Horizon
%\textit{include graphic or table showing increasing uncertainty with rising horizons}\\ 
\begin{columns}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figures/cilength_byhorizon.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\centering
\textbf{Average length of intervals}
\begin{table}
\begin{tabular}{ l c c }
&   50\%  & 80\%\\[0.3em]
\multicolumn{3}{c}{\textbf{GDP Growth}}\\
Fall,  SY & 0.5 & 1.1\\ 
Spring, SY &1.0 &2.1 \\ 
Fall, NY & 1.7 & 3.3\\ 
Spring, NY &2.1 &4.0 \\[0.3em] 
\multicolumn{3}{c}{\textbf{Inflation}}\\
%&   50\%  & 80\%\\[0.3em]
Fall,  SY & 0.3 & 0.5\\ 
Spring, SY &0.6 &1.2 \\ 
Fall, NY & 1.2 & 2.0\\ 
Spring, NY &1.4 &2.2 \\ 
\end{tabular}
\end{table}
\vspace{1.25cm}
\end{column}
\end{columns}

@@

\begin{frame}{Robustness Checks / Alternative Methods}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \begin{itemize}
    \item similar scores, worse calibration \hyperlink{errorextraction}{\beamerbutton{link}}
    \end{itemize}
    \item window method: rolling vs. expanding window
    \begin{itemize}
    \item slightly improved coverage and scores, at the cost of interpretability \hyperlink{extractionmethod}{\beamerbutton{link}}
    \end{itemize}

@@

\begin{frame}{Expanding Window - Scores}
\label{extractionmethod}
\end{frame}

\begin{frame}{Alternative truth value - Scores}
\label{alternativetruth}
    \begin{figure}
        %\centering
        \includegraphics[width=0.55\textwidth]{figures/oecdvsimf.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}   
\end{frame}

\begin{frame}{Alternative BVAR specification - Scores}
\label{alternativebvar}
\begin{figure}
  \begin{subfigure}{0.45\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/ho_bvarspecs_wis_pcpi_pch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
    \caption{Inflation}
  \end{subfigure}
  \hspace*{8mm}
  %\hfill  % maximize separation between the subfigures
  \begin{subfigure}{0.45\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/ho_bvarspecs_wis_ngdp_rpch_absolute_rollingwindow.pdf} %\vspace{0.3cm}
    \caption{GDP Growth}
  \end{subfigure}%
\end{figure}
\end{frame}

>>>>

\section{Results}
\begin{frame}{Scores on holdout data 2013-2023 - Inflation}
    \begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/wis_pcpi_pch_ho.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

\begin{frame}{Scores on holdout data 2013-2023 - GDP Growth}
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/wis_ngdp_rpch_ho.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

\begin{frame}{Calibration - on holdout data 2013-2023}
\begin{figure}
  \begin{subfigure}{0.385\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/coverage_pcpi_pch_ho.pdf} %\vspace{0.3cm}
  \end{subfigure}
  \hspace*{12mm}
  %\hfill  % maximize separation between the subfigures
  \begin{subfigure}{0.385\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/coverage_ngdp_rpch_ho.pdf} %\vspace{0.3cm}
  \end{subfigure}%
\end{figure}

@@

\begin{frame}{Increasing Uncertainty}
\begin{columns}
\begin{column}{0.6\textwidth}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{figures/cilength_byhorizon_ho.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}
\end{column}
\begin{column}{0.4\textwidth}
\centering
\textbf{Average length of intervals}
\begin{table}
\begin{tabular}{ l c c }
&   50\%  & 80\%\\[0.3em]
\multicolumn{3}{c}{\textbf{GDP Growth}}\\
Fall,  SY & 0.5 & 1.1\\ 
Spring, SY &1.0 &2.1 \\ 
Fall, NY & 1.7 & 3.3\\ 
Spring, NY &2.1 &4.0 \\[0.3em] 
\multicolumn{3}{c}{\textbf{Inflation}}\\
%&   50\%  & 80\%\\[0.3em]
Fall,  SY & 0.3 & 0.5\\ 
Spring, SY &0.6 &1.2 \\ 
Fall, NY & 1.2 & 2.0\\ 
Spring, NY &1.4 &2.2 \\ 
\end{tabular}
\end{table}
\vspace{1.25cm}
\end{column}
\end{columns}

@@

\begin{frame}{Robustness Checks / Alternative Methods}
\begin{itemize}
    \item error extraction method: absolute vs. directional errors
    \begin{itemize}
    \item similar scores, worse calibration \hyperlink{errorextraction}{\beamerbutton{link}}
    \end{itemize}
    \item window method: rolling vs. expanding window
    \begin{itemize}
    \item slightly improved coverage and scores, at the cost of interpretability 
    \end{itemize}

@@

\begin{frame}{Alternative truth value - Scores}
\label{alternativetruth}
    \begin{figure}
        %\centering
        \includegraphics[width=0.55\textwidth]{figures/ho_oecdvsimf.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
        \label{fig:enter-label}
    \end{figure}   
\end{frame}

\begin{frame}{Alternative BVAR specification - Scores}
\label{alternativebvar}
\begin{figure}
  \begin{subfigure}{0.45\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/bvarspecs_wis_pcpi_pch_ho.pdf} %\vspace{0.3cm}
    \caption{Inflation}
  \end{subfigure}
  \hspace*{8mm}
  %\hfill  % maximize separation between the subfigures
  \begin{subfigure}{0.45\textwidth}
  \centering
    \includegraphics[width=\textwidth]{figures/bvarspecs_wis_ngdp_rpch_ho.pdf} %\vspace{0.3cm}
    \caption{GDP Growth}
  \end{subfigure}%
\end{figure}
\end{frame}
